Haskell in Computational Biology

### 2013-04-28 jfp.tex
jfp draft with notes

\documentclass[compmod]{jfp1}

@@

\author[N. M. Daniels, A. Gallant, and N. Ramsey]
        {Noah M. Daniels \and Andrew Gallant \and Norman Ramsey \\
           {Department of Computer Science, Tufts University}\\
           {\email{{\rmfamily\{}ndaniels, agallant, nr{\rmfamily\}}@cs.tufts.edu}}}

@@

>>>>

\documentclass[]{jfp1}

@@

\author[N. M. Daniels, A. Gallant, and N. Ramsey]
        {Noah M. Daniels, Andrew Gallant, and Norman Ramsey \\
           {Department of Computer Science, Tufts University}\\
           {\email{{\rmfamily\{}ndaniels, agallant, nr{\rmfamily\}}@cs.tufts.edu}}}

@@

\section{Notes on the new paper}

\input{jfpnotes}
